\LARGE \bf A Pipeline to Assemble Near-Accident Footage Datasets

### 2020-10-22 paper.tex

@@

%\begin{center}
%\begin{tikzpicture}
%\begin{axis}[
%  title={Example histogram},
%  xlabel={Classes},
%  ylabel={$\textup{Normal}(\mu=0, \sigma=1)$}
%]
%\addplot[fill, ybar] table [x=X, y=Y, col sep=comma] {example.csv};
%\end{axis}
%\end{tikzpicture}
%\end{center}

>>>>

\tikzset{
    module/.style={%
        draw, rounded corners,
        minimum width=#1,
        minimum height=7mm,
        font=\sffamily
        },
    module/.default=2cm,
    >=LaTeX
}
\begin{tikzpicture}[
  % This will show the frame around the figure
  show background rectangle]

  % Place first 6 items
  \node[module] (crawler) {Web-Scrapers};
  \node[module, below=of crawler] (downloader) {Downloaders};
  \node[module, below=of downloader] (splitter) {Video-Splitter};
  \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
  \node[module, below=of labeller] (face-blur) {Face Blurring};
  \node[module, below=of face-blur] (license-blur) {License Plate Blurring};
  \node[draw,inner xsep=4mm,inner ysep=7mm,fit=(face-blur)(license-blur)](anon){};
  \node[anchor=north west,inner sep=1pt] at (anon.north west) 
    {Anonymization};
  \node[module, below=of anon] (uploader) {Data-Uploader};
  \draw[->] (crawler)--(downloader);
  \draw[->] (downloader)--(splitter);
  \draw[->] (splitter)--(labeller);
  \draw[->] (labeller)--(face-blur);
  \draw[->] (face-blur)--(license-blur);
  \draw[->] (license-blur)--(uploader);

\end{tikzpicture}

@@

%\begin{center}
%\begin{tikzpicture}
%\begin{axis}[
%  title={Example histogram},
%  xlabel={Classes},
%  ylabel={$\textup{Normal}(\mu=0, \sigma=1)$}
%]
%\addplot[fill, ybar] table [x=X, y=Y, col sep=comma] {example.csv};
%\end{axis}
%\end{tikzpicture}
%\end{center}
\pgfplotstableread[col sep=comma]{by-classes.csv}\byclass

\begin{center}
\begin{tikzpicture}
\begin{axis}[
  title={Objects by class},
  xlabel={Class},
  ylabel={Frequency (\# of bounding boxes)},
  xtick=data,
  xticklabels from table={\byclass}{X}
]
\addplot[fill, ybar] table [x expr=\coordindex, y={Y}] \byclass;
\end{axis}
\end{tikzpicture}
\end{center}

\begin{center}
\begin{tikzpicture}
\begin{axis}[
  title={Example histogram},
  xlabel={Classes},
  ylabel={$\textup{Normal}(\mu=0, \sigma=1)$}
]
\addplot[fill, ybar] table [x=X, y=Y, col sep=comma] {example.csv};
\end{axis}
\end{tikzpicture}
\end{center}
